Abstract Binding Trees

### 2015-10-25 paper.tex
Add wf-refinement rules for judgments and telescopes

Because we have not committed to using the built-in binding machinery to
express the well-scopedness of telescopes and sequents, we are free to use
\emph{symbols} in order to model the variables in the context. This is actually
quite sensible if we are trying to actually faithfully represent the syntax of
telescopes and sequents, rather than replace them with their counterparts on the
meta-level. It is certainly not intended that we should be able to take a
context $\Match{\Gamma}{x:A}$ and apply the substitution
$\IsSubst{M}{x}{\Gamma}{M:A}$, which is nonsensical; on the other hand, if $x$
had been a \emph{symbol}, all we could do is rename it in the context, since
substitution is not defined for symbols.

@@

Terms written using the abstract syntax will be difficult to read, so let us
define some notation:
\begin{align*}
  \IMode{\diamond} &\triangleq \OMode{\OpNil}\\
  \IMode{\Gamma, u:P} &\triangleq \OMode{
    \App{\OpSnoc{u}}{\Gamma, P}
  }\\
  \IMode{\Gamma\gg P} &\triangleq \OMode{
    \App{\OpSequent}{
      \Gamma, P
    }
  }\\
  \IMode{`u} &\triangleq \OMode{\OpVar{u}}
\end{align*}

@@

>>>>

Because we have not committed to using the built-in binding machinery to
express the well-scopedness of telescopes and sequents, we are free to use
\emph{symbols} in order to model the variables in the context. This is actually
quite sensible if we are trying to actually faithfully represent the syntax of
telescopes and sequents, rather than replace them with their counterparts on the
meta-level. It is certainly not intended that we should be able to take a
context $\Match{H}{x:A}$ and apply the substitution
$\IsSubst{M}{x}{H}{M:A}$, which is nonsensical; on the other hand, if $x$
had been a \emph{symbol}, all we could do is rename it in the context, since
substitution is not defined for symbols.

@@

Terms written using the abstract syntax will be difficult to read, so let us
define some notation:
\begin{align*}
  \IMode{\diamond} &\triangleq \OMode{\OpNil}\\
  \IMode{H, u:P} &\triangleq \OMode{
    \App{\OpSnoc{u}}{H, P}
  }\\
  \IMode{H\gg A} &\triangleq \OMode{
    \App{\OpSequent}{
      H, A
    }
  }\\
  \IMode{`u} &\triangleq \OMode{\OpVar{u}}
\end{align*}

@@

For the sake of this example, we will just stipulate that anything of sort $\SortExp$ or $\SortType$ is
grammatical:
\begin{align*}
  \infer{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{A}{\SortType}
  }{
  }\qquad
  \infer{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{M}{\SortExp}
  }{
  }
\end{align*}

The refinements for parametric judgment and sequents simply delegate to their
subterms:
\begin{gather*}
  \infer{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{
      \App{\OpNabla{\vec{s}}}{
        \MkBTm{\vec{u}}{}{J}
      }
    }{\SortJdg}
  }{
    \IsWf{\Omega}{\Upsilon,\vec{u}:\vec{s}}{\Gamma}{J}{\SortJdg}
  }\\[6pt]
  \infer{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{
      H\gg A
    }{\SortJdg}
  }{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{H}{\SortTele} &
    \IsWf{\Omega}{\Upsilon}{\Gamma}{A}{\SortType}
  }
\end{gather*}

The refinement for telescopes proceeds by induction:
\begin{gather*}
  \infer{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{\diamond}{\SortTele}
  }{
  }
  \qquad
  \infer{
    \IsWf{\Omega}{\Upsilon}{\Gamma}{H,u:A}{\SortTele}
  }{
    \begin{array}{l}
      \IsWf{\Omega}{\Upsilon\setminus\MkSet{u}}{\Gamma}{H}{\SortTele}\\
      \IsWf{\Omega}{\Upsilon\setminus\MkSet{u}}{\Gamma}{A}{\SortType}
    \end{array}
  }
\end{gather*}
